---
title: "RLohiya Discussion11"
author: "Ritesh Lohiya"
date: "November 6, 2018"
output: html_document
---

#                             Discussion 11

#           IS 605 FUNDAMENTALS OF COMPUTATIONAL MATHEMATICS

#                       Linear Regression Model



#Assignment: Using R, build a  regression model for data that interests you.  Conduct residual analysis.  Was the linear model appropriate? Why or why not?


I just created my own salary data and tried to fit the linear regression model. The Data has 2 columns years of experience and salary.

```{r}
#Salary data
salary <- read.csv('https://raw.githubusercontent.com/Riteshlohiya/Data605_Discussion11/master/Salary_Data.csv')
salary
summary(salary)
```

```{r}
#Distribution
hist(salary$YearsExperience, main = "Histogram of Years of Experience")
hist(salary$Salary, main = "Histogram of Years of Salary")
plot(salary$YearsExperience ~ salary$Salary, main = "Years of Experience vs Salary")
```

Craete a simple regression model:

```{r}
# Simple linear regression model
slm <- lm(salary$YearsExperience ~ salary$Salary)
summary(slm)
```

```{r}
plot(salary$YearsExperience ~ salary$Salary, 
     xlab='Salary',
     ylab='Years of Experience',
     main='Years of Experience vs Salary')
abline(slm)
```

Residual plots:

```{r}
# Residuals
plot(slm$residuals, ylab='Residuals')
abline(a=0, b=0)
```

```{r}
# Q-Q plot
qqnorm(slm$residuals)
qqline(slm$residuals)
```

#Conclusion:

The R-squared value is 95.7% which is good. That means that the explained variability is 95.7 % between independent and dependent variables. Seeing the residual plot, we can see there is constant variability and no pattern. Q-Q plot also looks good with some outliers at the tails. I think this linear model is appropriate.

